Predicting the 2024 U.S. Presidential Election: Trump’s Likely Victory Based on Polling Analysis

### 2024-11-03 paper/paper.qmd
committing text changes

- $ \text{Trump\_pct}_i $ and $ \text{Harris\_pct}_i $ are the polling support levels for Donald Trump and Kamala Harris in state $ i $.
- $ f(\text{end\_date\_num}_i) $ is a natural spline function of time (measured as `end_date_num`), with 4 degrees of freedom, capturing the non-linear time trends in support.
- $ \alpha_{\text{Trump}} $ and $ \alpha_{\text{Harris}} $ are intercepts for the models, representing the baseline support levels for each candidate.
- $ u_{\text{state}}^{\text{Trump}} $ and $ u_{\text{state}}^{\text{Harris}} $ are state-level random effects, accounting for differences in baseline support across states.

@@

# Display state predictions i n table
knitr::kable(state_summary_table) %>%
  kable_styling(full_width = FALSE, position = "center")

>>>>

- $ \text{Trump\_pct}_i $ and $ \text{Harris\_pct}_i $ are the polling support levels for Donald Trump and Kamala Harris in state $ i $.
- $ f(\text{end\_date\_num}_i) $ is a natural spline function of time (measured as $ \text{end\_date\_num} $), with 4 degrees of freedom, capturing the non-linear time trends in support.
- $ \alpha_{\text{Trump}} $ and $ \alpha_{\text{Harris}} $ are intercepts for the models, representing the baseline support levels for each candidate.
- $ u_{\text{state}}^{\text{Trump}} $ and $ u_{\text{state}}^{\text{Harris}} $ are state-level random effects, accounting for differences in baseline support across states.

@@

# Display state predictions i n table
knitr::kable(state_summary_table)
